HPC--101\\Onboarding

### 2017-07-18 hpc_101/sections/02_cluster.tex
update of what nodes are installed

  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{|l|l|l|l|l|l|l|l|}
        \multicolumn{8}{c}{ {\large {\textbf{ Condo Nodes}\textsuperscript{\ref{node_note}} } }} \\ \hline
        \textbf{Type} & \textbf{Cores} & \textbf{Ivy-Bridge} & \textbf{Haswell} & \textbf{Broadwell} & \textbf{128 GB}\textsuperscript{\ref{mem_limit}} & \textbf{256 GB}\textsuperscript{\ref{mem_limit}} & \textbf{1 TB}\textsuperscript{\ref{mem_limit}} \\ \hline
        Standard & 24 & & 62 & & 62 & & \\ \hline
        Standard & 20 & & & 5 & 5 & & \\ \hline
        Custom & 20 &  & 33 $+$ (4)\footnote{\label{future}\tiny June 2017 additions} & &  & 33 & (4)\textsuperscript{\ref{future}} \\ \hline
        GPU\textsuperscript{\ref{gpu_v1}}     & 20 &  & 1 &  & 1 &  &  \\ \hline
      \end{tabular}%
    }
    \end{table}
  \end{frame}

>>>>

  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{|l|l|l|l|l|l|l|l|}
        \multicolumn{8}{c}{ {\large {\textbf{ Condo Nodes}\textsuperscript{\ref{node_note}} } }} \\ \hline
        \textbf{Type} & \textbf{Cores} & \textbf{Ivy-Bridge} & \textbf{Haswell} & \textbf{Broadwell} & \textbf{128 GB}\textsuperscript{\ref{mem_limit}} & \textbf{256 GB}\textsuperscript{\ref{mem_limit}} & \textbf{1 TB}\textsuperscript{\ref{mem_limit}} \\ \hline
        Standard & 24 & & 62 & & 62 & & \\ \hline
        Standard & 20 & & & 5 & 5 & & \\ \hline
        Custom & 20 &  & 37 & &  & 33 & 4 \\ \hline
        GPU\textsuperscript{\ref{gpu_v1}}     & 20 &  & 1 &  & 1 &  &  \\ \hline
      \end{tabular}%
    }
    \end{table}
  \end{frame}
